### 2020-04-30 final_report/conclusion.tex
rename Nikos in acknowledgements

The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
Konstantinidis, Nikos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
Waldmann for their supervision and valuable suggestions related to this work.

>>>>

The authors would like to thank Vignesh Gopakumar, Prof.~Nikolaos
Konstantinidis, Nikolaos Nikolaou, Prof.~Emily Nurse, Jonathan Shimwell and Ingo
Waldmann for their supervision and valuable suggestions related to this work.
